Context Inconsistency Management \\Using Partial Constraint Checking

### 2011-03-03 paper/paper.tex
tweak

In this article we aim at putting a milestone for context management by proposing an efficient inconsistency detection algorithm based on a constraint language extending the traditional ontology based context model. In addition we put forward a conflict resolution algorithm which is based on a context reliability heuristic. Finally the use of fuzzy ontologies representing context inconsistencies as a promising alternative to conflict resolution is explored.

>>>>

In this article we aim at putting a milestone for context management by presenting an efficient inconsistency detection algorithm based on a constraint language extending the traditional ontology based context model~\cite{xu:2010:PCC}. In addition we put forward a conflict resolution algorithm which is based on a context reliability heuristic~\cite{bu:2006:CCM}. Finally the use of fuzzy ontologies representing context inconsistencies as a promising alternative to conflict resolution is explored.
